TBD

### 2021-03-23 outputs/paper/paper.Rmd
revert last changes to s8 model
RMSE model validation completed

# Results

@@

# code dummy variables
s8_model <- dfBehavModel %>%
  mutate(no_money = if_else(cond == 0, 1, 0)) %>%
  mutate(money = if_else(cond != 0, 1, 0))

>>>>

```{r model checks, echo = FALSE, message = FALSE, warning = FALSE}

### S8/Table 1 (main result)

s8_model <- dfBehavModel %>%
  filter(cond != 0)
s8_model$cond <- ifelse(s8_model$cond == 1, 0, 1)

s8_main_result <- lm(response ~ cond, data = s8_model)
s8_money_result <- lm(response ~ cond + male + above40 + computer + coworkers + other_bystanders, data = s8_model)

  # RMSE
s8_rmse <- c(sqrt(mean(s8_main_result$residuals^2)),
            sqrt(mean(s8_money_result$residuals^2)))

```{r s9modelcheck}

### S9 (main result)

s9_main <- dfBehavModel %>%
  filter(country == 39 | country == 27 | country == 40) %>%
  mutate(money = if_else(cond == 1, 1, 0)) %>%
  mutate(big_money = if_else(cond == 2, 1, 0))

  # RMSE
s9_rmse <- c(sqrt(mean(s9_main_result$residuals^2)),
            sqrt(mean(s9_uk_result$residuals^2)),
            sqrt(mean(s9_poland_result$residuals^2)),
            sqrt(mean(s9_usa_result$residuals^2)))

```{r s10modelcheck, echo - FALSE, warning = FALSE, messages = FALSE}
### S10/Table 3 (main result)

s10_main <- dfBehavModel %>%
  filter(country == 39 | country == 27 | country == 40)
s10_main$cond <- ifelse(s10_main$cond == 3, 1, 0)

s10_main_result <- lm(response ~ cond, data = s9_main)
  # UK
s10_uk <- s9_main %>%
  filter(country == 39)
s10_uk_result <- lm(response ~ cond, data = s10_uk)

# RMSE
s10_rmse <- c(sqrt(mean(s10_main_result$residuals^2)),
              sqrt(mean(s10_uk_result$residuals^2)),
              sqrt(mean(s10_poland_result$residuals^2)),
              sqrt(mean(s10_usa_result$residuals^2)))

```
# Results

@@

# code dummy variables
s8_model <- dfBehavModel %>%
  filter(cond != 0)
s8_model$cond <- ifelse(s8_model$cond == 1, 0, 1)
